---
title: Lab 04
author: YOUR NAME GOES HERE
output:
  html_document
---

Due: Friday, October 4, 11:59pm.

Remember to load in any required packages and data. We'll do that in an
initial chunk here (fill in the file path and required packages). Note the options for suppressing messages and warnings in the knitted document, which prevents a lot of  unnecessary text from appearing in your final .html page.

### Exercise 1

```{r loading, message = F, warning = F}
# load library here

# load in data here
```

### Exercise 2

```{r ex-2}

```

### Exercise 3

```{r ex-3}

```

### Exercise 4

```{r ex-4}

```

### Exercise 5

...and so on. Be careful to have proper line spacing around exercises, and
also be careful not to duplicate chunk names (your document won't knit if any
exist). Insert R chunks and narrative answers as appropriate. Remember to
show all work/code used for full credit.

### Exercise 6


### Exercise 7



Remember to knit your lab into an .html file and then save it as a .pdf in a 
web browser. 
