---
title: Lab 01
author: Solution
date: "Due: Friday, August 23, 2024 at 11:59PM"
output:
  html_document
---

(2 points per question, total 12 points)

```{r data-and-packages, warning = F, message = F}

# You may need to install the tidyverse packages, which you can do by running
# the following line of code in the Console:

# install.packages("tidyverse")

library(tidyverse)

cdc <- read.csv("https://karamccor.github.io/b6002/labs/data/cdc_cleaned.csv")
```

#### Exercise 1

```{r}
ggplot(data = cdc, mapping = aes(x = Exercise,y = Obesity,color = HDI, shape = HDI)) + 
  geom_point()
```

For those in the Bottom ten HDI, more individuals tend to be obese, and these are also the states getting less adequate aerobic activity.


#### Exercise 2

```{r ex-2}
ggplot(data = cdc, mapping = aes(x = Region)) + 
  geom_bar(fill = "pink") + 
  labs(title = "Number of US States by Census Region", 
       x = "Region", y = "Count")
```

#### Exercise 3

```{r ex-3}
ggplot(data = cdc, aes(x = Smoking)) +
  geom_histogram(color = "darkblue", fill = "lightblue", binwidth = 2)+ 
  labs(title = "Distribution of Adult Smoking (%) by State", 
       x = "Adult Smoking (%)", y = "Count")
```

It looks like most states have between 30-22% smokers in that state. Very few states have 10% smokers or below. 

#### Exercise 4

```{r ex-4}
ggplot(data = cdc, mapping = aes(x = FluVaccination, y = ChildVaccination)) + 
  geom_point() +
  labs(title = "Flu Vaccination rate (%) vs. Child Vaccination rate (%)", 
       x = "Flu Vaccination rate (%)", y = "Child Vaccination rate (%)")
```

There seems to be a slight increase in child vaccination rate as general flu vaccination rate increases.

#### Exercise 5

```{r ex-5}
ggplot(data = cdc, mapping = aes(x = CVDeathRate, y = Obesity, color = HDI)) + 
  geom_point() +
  labs(title = "CV Death Rate (%) vs. Obesity by State HDI", 
       x = "CV Death Rate (%)", y = "Obesity (%)")
```

States in the bottom ten HDI have the highest CV death rates and the highest obesity rates. In general, there is an upward trend between CV death rates and Obesity. 

#### Exercise 6

```{r ex-6}
ggplot(data = cdc, mapping = aes(x = Smoking, y = Obesity, color = HDI)) + 
  geom_point() +
  labs(title = "Smoking rate (%) vs. Obesity by State HDI", 
       x = "Smoking rate (%)", y = "Obesity (%)")
```

Similar to the previous plot, the smoking rate and obesity rate have a positive trend across states. Additionally, those states in the bototm ten HDI have the highest smoking rates and highest obesity rates.
