---
title: HW 02
author: YOUR NAME GOES HERE
date: "Due: Wednesday, September 19, 2024 at 11:59PM"
output:
  html_document
---

#### Exercise 1:

```{r, ex-1}
# You may do a calculation here, for instance, as follows:

1+1

# Any R code preceded by a pound sign (#) is a comment, and is not evaluated. Delete any R Comments before knitting your document!
```

#### Exercise 2:

```{r, ex-2}
# You may do a calculation here, for instance, as follows:

(0.25*0.25)^3/(1 + 3)

# Don't forget to delete comments!
```

#### Exercise 3:

```{r, ex-3}

```

#### Exercise 4:

In `R` markdown documents, we may also directly write narratives explaining our answers. In this space, explain why $A$ and $B$ are, or are not, independent events.

#### Exercise 5:

Do Exercise 5 here. Feel free to write out any numerical calculations you are using. In doing so, set numerical expression in your narrative using backticks. For instance, `(0.3)*(0.4) = 0.12`.

#### Exercise 6:

Do Exercise 6 here. Feel free to write out any numerical calculations you are using, setting them apart using backticks in order to draw attention to them. For instance, `(0.1 * 0.2)/(0.4*0.6 + (1-0.4)*0.3)`. When displaying your final answer, use an `R` chunk to evaluate the answer:

```{r, ex-6}

```

#### Exercise 7:

Do Exercise 7 here. Use the narrative space to explain your work. For example, `P(A) = 0.5` (note that the previous expression was set apart using backticks). To have `R` evaluate a numeric term, create an `R` chunk as in the template above. Be sure to give it a meaningful name!

#### Exercise 8:

...and so on.

#### Exercise 9:

#### Exercise 10:

#### Exercise 11:

#### Exercise 12:

#### Exercise 13:

#### Exercise 14:

#### Exercise 15:

```{r, ex-15-load-data}
# Load your data here using the code in the homework. Remember to delete this comment!
```

```{r, ex-15-packages, message = FALSE, warning = FALSE}
# Loading in tidyverse package...
library(tidyverse)
```

```{r, ex-15-histogram}
# Create your histogram using ggplot here. Do not use base R graphics, use ggplot2 graphics, as in lab.
```

Write your narrative here!

#### Exercise 16:
